Plant-pollintor networks worldwide are composed by the same specific building

### 2021-09-28 Draft/Draft.Rmd
Edit on figure 2, hopefully better now?

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=9,fig.height=5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks. This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (coloured dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation). The different motifs are coloured by the four categories of path length determined in Simmons et al. (2020)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
                 color = as.factor(Broad_categories)),
             position = "jitter",alpha=0.8)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
                size=2)+
  labs(y="Two to five node motifs", x = "Percentile",colour="Path length classification")+
  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey36","lightblue3","navajowhite2","darkorange4"),guide = guide_legend(title.position = "top",ncol = 1)) +
theme(legend.text.align = 0)+
  theme(legend.position="right")
#Trying to maintain a gradient from low to high in colors

@@

Although motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**), we found differences in the average percentile within floral visitors and pollinators functional groups (columns in **Figure 3**). Remarkably, the same patterns were observed but with lower average percentiles when singletones were exluded (**Figure S2**). Thus,

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="**Figure S1.** Comparison of the motif frequencies between empirical and simulated networks excluding singletones. Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one. The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
                 color = as.factor(Broad_categories)),
             position = "jitter",alpha=0.8)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
                size=2)+
  labs(y="Two to five node motifs", x = "Percentile",colour="Path length classification")+
  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey36","lightblue3","navajowhite2","darkorange4"),guide = guide_legend(title.position = "top",ncol = 1)) +
theme(legend.text.align = 0)+
  theme(legend.position="right")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks divided by average path length (plots a, b, c and d) as determined in Simmons et al. (2020). This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

#Ffilter out two node motifs
d_1 <- d %>% filter(motif != 1)
#Merge dataframes to bl able to create facets
d_2 <- merge(d_1, motif_means, by="motif")

arr <- list('Strong' = expression(bold(paste("(a) Complete (strong, ", bar(x), " = 1.38)"))),
             'Fan' = expression(bold(paste("(b) Fan (medium-strong, ", bar(x), " = 1.48)"))), 
             'Medium-weak' = expression(bold(paste("(c) Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
             "Weak" =expression(bold(paste("(d) Core-peripheral (weak, ", bar(x), " = 1.85)"))))
mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }

library(ggforce) #workaround with ggforce to have facets with same sizes

p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=1)+
  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
                width=0.8,size=0.8,color="black") +theme_bw()+
  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
  theme( strip.background = element_blank())+
  theme(strip.text = element_text(face="bold", size=10, hjust=0),
        panel.border=element_rect(color="black",size=1.2))

p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)

@@

Although motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**), we found differences in the average percentile within floral visitors and pollinators functional groups (columns in **Figure 3**). These differences were more marked for floral visitors functional groups. Bees had a tendency to be over-represented in the different motif positions. This was also observed in lower degree for non-syrphids Diptera. In contrast, Lepidoptera were generally under-represented in the different motif positions and non-bee hymenoptera showed also the same tendency but with lower average percentiles. For plants, these differences across functional groups were less marked.

@@

  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
                                      "Non-syrphids\nDiptera","Syrphids")
}else{
  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="**Figure S1.** Comparison of the motif frequencies between empirical and simulated networks excluding singletones. Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one. The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=4.5,fig.height=6.5}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

#Ffilter out two node motifs
d_1 <- d %>% filter(motif != 1)
#Merge dataframes to bl able to create facets
d_2 <- merge(d_1, motif_means, by="motif")

arr <- list('Strong' = expression(bold(paste("Complete (strong, ", bar(x), " = 1.38)"))),
             'Fan' = expression(bold(paste("Fan (medium-strong, ", bar(x), " = 1.48)"))), 
             'Medium-weak' = expression(bold(paste("Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
             "Weak" =expression(bold(paste("Core-peripheral (weak, ", bar(x), " = 1.85)"))))
mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }

library(ggforce) #workaround with ggforce to have facets with same sizes

p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=2, alpha=1)+
  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
                width=1.0,size=1,color="grey20") +theme_bw()+
  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
             size=2,color="grey20")+labs(y="Two to five node motifs", x = "Percentile")+
  theme( strip.background = element_blank())+
  theme(strip.text = element_text(face="bold", size=10, hjust=0),
        panel.border=element_rect(color="black",size=1.2))

p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
